---
title: "riksdagenvignette"
author: "Chao Fu & Michael Bailey"
data: "r Sys.Date()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{riksdagenvignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(riksdagen)
```
# Description
The function creates an API connecting to website to get the data of voting in different parties and makes some basic analysis.

# Functions

## riksdagen
1. The input is a character and format is "2012/13".
1. The range of the input is from "2020/21" to "2002/2003".
1. The return is a data.frame with some basic analysis.

## runRiksShiny
1. The function searches the riksdagen package directory to locate a folder called "ShinyApp". It then uses shiny::runApp to run the shiny app from that directory. It takes no arguments.

# Usage

## Install

```{r, eval=FALSE}
devtools::install_github("chafu696/Lab5")

```

## Example

```{r, eval=FALSE}
users <- riksdagen("2020/21")
print(users)

```
